%-------------------------
% Resume in Latex
% Author : Subhrato Som
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
 \usepackage[default]{lato}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.8in}
\addtolength{\textwidth}{1.39in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.6in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\vspace{-16pt}
\begin{center}
    {\Huge \scshape Subhrato Som} \\ \vspace{1pt}
    Philadelphia, Pennsylvania 19104 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 215-240-9510 ~ \href{mailto:ss5654@drexel.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{ss5654@drexel.edu}} ~ 
    \href{https://linkedin.com/in/subhratosom/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/subhratosom/}}  ~
    \href{https://github.com/Subhrato20}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Subhrato20}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Drexel University}{Sep 2023 - May 2025}
      {Master's of Science in Computer Science}{Philadelphia, PA, USA}

    \vspace{-5pt}
    \resumeSubheading
      {Vellore Institute of Technology}{Jul 2019 - Jun 2023}
      {Bachelor of Technology in Computer Science and Engineering}{Chennai, TN, India}
  
  \resumeSubHeadingListEnd
  \vspace{0.2em}
    \hspace{0.15in}\begin{tabular}{p{0.94\linewidth}}
    \textit{{Coursework}: Machine Learning, Deep Learning, Computer Vision, Data Structures \& Algorithms, Software Design, Test Driven Development, Computer Architecture \& Organization Full Stack, Agile Methodology, Object Oriented Programming, Operating Systems, Information Security Database Management, DevOps, CI/CD.}
\end{tabular}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Cloud Technologies}{: AWS EC2, AWS SageMaker, AWS Lambda, Docker, Jenkins, Kubernetes.} \\
		\textbf{Languages}{: Python, Java, JavaScript, Matlab, Swift, Julia, Rust, C, C++.} \\
		\textbf{Web Development}{: HTML, CSS, React, Node.js, Express.js, Flask.} \\
		\textbf{Machine Learning}{: Scikit-learn, TensorFlow, PyTorch, LangChain.} \\
		\textbf{Database Technologies}{: MySQL, PostgreSQL, MongoDB, Snowflake}\\
            \textbf{System Designs}{: Distributed Systems, Object-Oriented Design, Scalability}}
	}
\end{itemize}
\vspace{-15pt}
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {AI Intern}{Jun 2024 -- Dec 2024}
    {Mathtech, Inc}{Hamilton, NJ}
    \resumeItemListStart
        \resumeItem{Developed, optimized and shipped a Retrieval-Augmented Generation (RAG) system, leveraging advanced natural language processing techniques for efficient document retrieval and knowledge generation.}
        \resumeItem{Utilized AWS services like SageMaker, EC2, and S3 for the system to ensure scalable and efficient deployment.}
        \resumeItem{Integrated AWS Cognito for secure user authentication and streamlined access management within the application.}
        \resumeItem{Developed a seamless pipeline for document storage, embedding generation, and vector search using SageMaker and Milvus hosted on EC2.}
        \resumeItem{Enhanced chunk parsing techniques by dynamically adjusting chunk size and overlap based on document structure, significantly improving contextual understanding and retrieval efficiency.}
        \resumeItem{Implemented chunk ranking using BERT-based models to score and prioritize document chunks, enhancing the relevance of retrieved information and ensuring better alignment with user queries.}

        \resumeItem{Designed and fine-tuned custom embeddings using dense and sparse vector representations to achieve superior retrieval performance.}
    \resumeItemListEnd
    \resumeSubheading
    {Research Assistant}{Feb 2024 -- Present}
    {Social-NLP Lab, CCI Drexel University}{Philadelphia, PA}
    \resumeItemListStart
        \resumeItem{Conducted in-depth research on substance abuse memes on Reddit under Prof. Rezvaneh (Shadi) Rezapour, aiming to identify trends and insights that inform academic understanding.}
        \resumeItem{Utilized state-of-the-art Large Language Models to analyze and interpret textual and visual elements, advancing the field of digital sociology.}
        \resumeItem{Worked on comparative analysis of LLaMA and GPT models, focusing on performance, efficiency, and application-specific strengths to derive actionable insights for research projects.}
        \resumeItem{Implemented batch API methods for GPT-based inference, significantly improving processing efficiency for large-scale textual datasets.}
        \resumeItem{Analyzed semantic understanding of discourse in drug-related memes, comparing them with non-drug meme communities and incorporating human evaluation to validate findings.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-15pt}


%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Disaster Risk Analytics Platform} $|$ \emph{Philly Codefest 2024, Chubb Challenge Winner}} {Apr 2024}
    \resumeItemListStart
        \resumeItem{Developed and led a Climate Risk Analysis Platform, winning first place at Philly Codefest's Chubb Challenge. Integrated Poisson’s distribution and deep learning models to assess disaster risk and predict financial damages with high precision.}
        \resumeItem{Built a responsive Flask-based web application deployed on AWS EC2, utilizing AWS S3 for data storage and scalability to handle high user traffic during disaster events.}
        \resumeItem{Incorporated real-time interactive map of United States for risk assessment.}
        \resumeItem{Collaborated with a multidisciplinary team to enhance user experience.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Image Captioning for Chest X-ray Image} $|$ \emph{Vellore Institute of Technology (Capstone Project)}} {Nov 2022 -- May 2023}
    \resumeItemListStart
        \resumeItem{Developed Encoder-Decoder models using TensorFlow-Keras, incorporating CNN architectures such as Xception, VGG16, and ResNet for accurate disease classification and automated captioning of chest X-ray images.}
        \resumeItem{Implemented Long Short-Term Memory (LSTM) networks for text generation, achieving seamless integration of visual and textual data.}
        \resumeItem{Improved diagnostic efficiency with 86.4\% accuracy in disease identification, significantly improving diagnostic efficiency and reducing error rates in radiographic reports.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Superhero Image generation Using Generative Adversarial Network} $|$ \emph{Vellore Institute of Technology}} {Jul 2022}
    \resumeItemListStart
        \resumeItem{Designed new superhero characters by leveraging StyleGAN to generate a diverse range of creative images, starting from a curated dataset of 150 existing superheroes.}
        \resumeItem{Implemented data preprocessing pipelines to clean, resize, and augment the dataset, ensuring optimal input for the StyleGAN model.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{REppeaR (Real Estate Transaction Website)} $|$ \emph{Vellore Institute of Technology}} {Mar 2022 -- Jun 2022}
    \resumeItemListStart
        \resumeItem{Developed "REppeaR," a blockchain-based real estate transaction website using NodeJS, EJS, JavaScript, HTML, CSS, and MongoDB. The system featured a JavaScript-based blockchain network for secure and transparent data transactions.}
        \resumeItem{Incorporated multi-user access system design (Admin and User) with robust authorization mechanisms to maintain data integrity and ensure secure transactions.}
        \resumeItem{Enhanced security through cryptographic hashing for user data and implemented a digital signature verification mechanism to validate transactions.}
        \resumeItem{Provided real-time transaction tracking and history, improving transparency in property dealings.}
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Question Answering System using BERT} $|$ \emph{Vellore Institute of Technology}} {Feb 2022 -- Apr 2022}
    \resumeItemListStart
        \resumeItem{Developed a question-answering system powered by BERT, trained on the CoQA dataset, and fine-tuned for contextual adaptability across diverse linguistic scenarios.}
        \resumeItem{Integrated pre-processing techniques like tokenization, padding, and truncation for efficient model training and inference.}
        \resumeItem{Achieved an accuracy of 84.1\% using cosine similarity for evaluation.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Activities-----------
\section{Activities}
\begin{tabular}{p{0.99\linewidth}}
    \hspace{0.15in}\textbf{Chubb Challenge Winner}, Philly Codefest 2024
        \hfill \textbf{Apr. 2024} \\
            \hspace{0.15in}\textbf{React Summit}, GitNataion
        \hfill \textbf{June 2022}\\
    \hspace{0.15in}\textbf{Open Source Contributor}, Girlscript Foundation
        \hfill \textbf{Sep. 2021 -- Dec 2021}\\

    \hspace{0.15in}\textbf{Student Expert}, Postman
        \hfill \textbf{Aug. 2021 -- Jul 2023} 
    
\end{tabular}
\vspace{-15pt}

%-----------CERTIFICATION-----------%
\section{Certifications}
\begin{tabular}{p{0.99\linewidth}}
    \hspace{0.15in}\textbf{PostgreSQL for Everybody}, University of Michigan
        \hfill \textbf{Feb. 2024} \\
    \hspace{0.15in}\textbf{Data Visualization with Tableau}, UC Davis (Coursera)
        \hfill \textbf{Feb. 2023} \\
    \hspace{0.15in}\textbf{REACT SUMMIT}, GitNation
        \hfill \textbf{Jun. 2022} \\
    \hspace{0.15in}\textbf{Microsoft Azure Fundamentals (AZ-900)}, Microsoft
        \hfill \textbf{May. 2022} \\
    \hspace{0.15in}\textbf{Google Data Analytics Professional Certification}, Google (Coursera)
        \hfill \textbf{Jan. 2022} \\
    \hspace{0.15in}\textbf{The Complete 2022 Web Development Bootcamp}, Udemy
        \hfill \textbf{Sep. 2021} \\
    \hspace{0.15in}\textbf{AI for Everybody}, Deeplearning.ai (Coursera)
        \hfill \textbf{Aug. 2021} \\
    \hspace{0.15in}\textbf{Fundamentals of Data Analytics}, Nasscom FutureSkills Prime
        \hfill \textbf{Aug. 2021} \\
    \hspace{0.15in}\textbf{Machine Learning A-Z: Hands-On Python and R In Data Science}, Udemy
        \hfill \textbf{Aug. 2021} \\
\end{tabular}

\end{document}
